---
title: "linreg"
author: "Chathuranga Silva & Mohammed Bakheet"
date: "24th September 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab04)
```

# Fitting Linear Models

``` linreg ``` is used to fit linear models. It can be used to carry out regression, variance and analysis of covariance.

# Usage

```c
 linreg(formula, data)
```

# Arguments

formula
  : an object of class ``` formula ``` (or one that can be coerced to that class): a symbolic description of the model to be fitted. The details of model specification are given under ‘Details’.
  
data
  : a vector specifying a subset of observations to be used in the fitting process.

# Value

An object of class ``` linreg ``` is a list containing at least the following components:

reg_coef
  : a named vector of coefficients
  
residuals
  : the residuals, that is response minus fitted values.
  
fitted_val
  : the fitted mean values.
  
degree_of_freedom
  : test
  
residul_variance
  : test
  
variance_reg_coef
  : test
  
t_value
  : test
  
p_value
  : test

# References

R packages by Hadley Wickham 

# Examples

```
item <- linreg(formula = Petal.Length~Species, data = iris)
item$print()
item$summary()

```

